Regional Base-Flow Index in Arid Landscapes Using Machine Learning and Instrumented Records

### 2025-01-13 MANUSCRIPT.qmd
Update MANUSCRIPT.qmd

|              | Variable                  | Source       | Geoprocessing          |
|----------------|----------------------|----------------|-------------------|
| Hydroclimate | Precipitation\*           | PRISM        | Basin average          |
|              | Mean Temperature\*        | PRISM        | Basin average          |
|              | Mean Evapotranspiration\* | TerraClimate | Basin average          |
| Geospatial   | Elevation\*               | DEM          | Basin average          |
|              | Area                      | DEM          | Basin average          |
|              | Slope                     | DEM          | Basin average          |
|              | Aspect                    | DEM          | Percent areal coverage |
|              | Land Cover\*              | NLCD         | Percent areal coverage |
|              | Hydrologic Soil Group\*   | SSURGO       | Percent areal coverage |
|              | Geology                   | USGS         | Percent areal coverage |
|              | Karst                     | USGS         | Percent areal coverage |

>>>>

|              | Variable                  | Source       | Geoprocessing          |
|-----------------|---------------------|-----------------|------------------|
| Hydroclimate | Precipitation\*           | PRISM        | Basin average          |
|              | Mean Temperature\*        | PRISM        | Basin average          |
|              | Mean Evapotranspiration\* | TerraClimate | Basin average          |
| Geospatial   | Elevation\*               | DEM          | Basin average          |
|              | Area                      | DEM          | Basin average          |
|              | Slope                     | DEM          | Basin average          |
|              | Aspect                    | DEM          | Percent areal coverage |
|              | Land Cover\*              | NLCD         | Percent areal coverage |
|              | Hydrologic Soil Group\*   | SSURGO       | Percent areal coverage |
|              | Geology                   | USGS         | Percent areal coverage |
|              | Karst                     | USGS         | Percent areal coverage |
